---
title: "interactive graph examples"
author: "Audrey Nolan"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, we will practice creating some interactive graphs and tables, using built-in datases in R packages. 

- Interactive plots: {plotly}
- Interactive tables: {DT}

(use include = FALSE for zeo errors/messages/etc to show up in the markdwon doc)

```{r, include = FALSE}

# Attach packages: 

library(tidyverse)
library(plotly)
library(DT)

```

### A. Interactive Graph of Iris Dimensions

Using Edgar Anderson's famous 'iris' dataset

echo = FALSE for this code chunk to not show up 
orrrr if not in the entire doc then do echo = FALSE in the options set up top
or use eval = FALSE to tell R not to evaluate this chuck rn, b/c it's not working properly

```{r, echo = FALSE}

iris_graph <- ggplot(data = iris, aes(x = Petal.Width, y = Petal.Length))+
  geom_point(aes(size = Sepal.Width, 
                 color = Species), 
             alpha = 0.5)+
  theme_minimal()+
  labs(title = "My  Iris Graph", x = "Petal Width (cm)", y = "Petal Length (cm)")

# iris_graph

ggplotly(iris_graph)

```


### Make an interactive table with DT

```{r}

datatable(msleep)

```

